Analysis of the 2005--\myrevision{2016} Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2017-06-22 seismicity.tex
done with main changes, conclusions pending

In addition to using $M_c$ to determine the $b$-value for each sub-catalog, we also use it as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graphs for each region. \myrevision{Table \ref{tab:seismicity} shows the number of events of the whole catalog, along with the number of events for each region's complete and declustered catalogs. It also includes the corresponding values of $M_c$, which happened to be the same for both catalogs, and the separate values of $b$, including the standard deviation, $\sigma_b$, which is calculated as}
% 
\begin{equation}
\myrevision{
	\sigma_b = 2.3 \, b^2 \sqrt{ \frac{ \sum_{i = 1}^{N} \left( M_i - \overline{M} \right)^2 }{ N \left(N - 1 \right) } } \, ,
}
\end{equation}
% 
\noindent
where $N$ is the number of events in each catalog \citep{Shi1982standard}.

>>>>

In addition to using $M_c$ to determine $b$ for each sub-catalog, we also use it as the threshold for limiting the minimum magnitude to be considered in the construction of the visibility graphs for each region. \myrevision{Table \ref{tab:seismicity} shows the number of events of the whole catalog, along with the number of events for each region's complete and declustered catalogs. It also includes the corresponding values of $M_c$, which happened to be the same for both catalogs, and the separate values of $b$, including the standard deviation, $\sigma_b$, which is calculated as}
% 
\begin{equation}
\myrevision{
	\sigma_b = 2.3 \, b^2 \sqrt{ \frac{ \sum_{i = 1}^{N} \left( M_i - \overline{M} \right)^2 }{ N \left(N - 1 \right) } } \, ,
}
\end{equation}
% 
\noindent
where $N$ is the number of events in each catalog \citep{Shi1982standard}.
